Supplemental Materials, Methods and Results

### 2021-05-09 supp.Rmd
Implemented all RVEs for models...some problems with convergence on a few achromatix models, odd. Need to check these. Add in tables now is all that is left.

 # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

  # Fit the interaction model
    CourtshipAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

  # Fit main effects model
    CourtshipAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
    summary(CourtshipAC)

  # Interaction needed? No
    anova(CourtshipAC_inter, CourtshipAC)

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC <- clubSandwich::coef_test(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

  # Planned contrasts / hypothesis tests. Need to fit model a little differently
    CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
    CourtshipBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = CourtshipBgrd)

   # Fit Robust model
    robust_CourtshipBgrd_pop_back <- clubSandwich::conf_int(CourtshipBgrd_pop_back, cluster = CourtshipBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_back <- Wald_test(CourtshipBgrd_pop_back, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_courtship_AC <- result_CourtshipBgrd_pop_back[2,8]
       CI_AC_Courtship <- data.frame(Estimate=robust_CourtshipBgrd_pop_back$beta[3],
                               lwr = robust_CourtshipBgrd_pop_back$CI_L[3],
                               upr = robust_CourtshipBgrd_pop_back$CI_U[3])

##########
# Chromatic - dS
##########
 # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

  # Fit interaction model
    CourtshipCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

  # Fit main effect model
      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)
      anova(CourtshipCC)

  # Test whether interaction is supported
    anova(CourtshipCC_inter, CourtshipCC)

@@

  # Planned comparions
    CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
  CourtshipBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = CourtshipBgrd)

     # Fit Robust model
    robust_CourtshipBgrd_pop_backCC <- clubSandwich::conf_int(CourtshipBgrd_pop_backCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_backCC <- Wald_test(CourtshipBgrd_pop_backCC, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_backCC$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_courtship_CC <- result_CourtshipBgrd_pop_backCC[2,8]
       CI_CC_Courtship <- data.frame(Estimate=robust_CourtshipBgrd_pop_backCC$beta[3],
                               lwr = robust_CourtshipBgrd_pop_backCC$CI_L[3],
                               upr = robust_CourtshipBgrd_pop_backCC$CI_U[3])

>>>>

  # Fit main effects model
    CourtshipAC <- lmer(dL ~ Population  + Background_pop + BodyRegion + (1|ID), data=CourtshipBgrd)
    summary(CourtshipAC)

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC <- clubSandwich::conf_int(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

           BodyRegion_AC_Court <- Wald_test(CourtshipAC, constraints = constrain_zero(4:6), 
                                  cluster = CourtshipBgrd$ID, vcov = "CR2")

  # Planned contrasts / hypothesis tests. Need to fit model a little differently
    CourtshipBgrd$pop_back_BR <- with(CourtshipBgrd, interaction(Population, Background_pop, BodyRegion))
    CourtshipBgrd_Hawaii <-CourtshipBgrd %>% filter(Population == "Hawaii")
    CourtshipBgrd_pop_back_BR <- lmer(dL ~ -1 + pop_back_BR + (1|ID), data = CourtshipBgrd_Hawaii)

   # Fit Robust model
    robust_CourtshipBgrd_pop_back_BR <- clubSandwich::conf_int(CourtshipBgrd_pop_back_BR, 
                                                            cluster = CourtshipBgrd_Hawaii$ID, 
                                                            vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE ********** PROBLEM WITH CONVERGENCE NON-POSITIVE DEF MATRICES
      result_CourtshipBgrd_pop_back_BR <- Wald_test(CourtshipBgrd_pop_back_BR, 
                                                 constraints = constrain_pairwise(c(1:8)), 
                                                 vcov="CR2", tidy = TRUE)

      result_CourtshipBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

##########
# Chromatic - dS
##########

  # Fit main effect model
      CourtshipCC <- lmer(dS ~ Population  + Background_pop + BodyRegion + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)

@@

           BodyRegion_CC_Court <- Wald_test(CourtshipCC, constraints = constrain_zero(4:6), 
                                  cluster = CourtshipBgrd$ID, vcov = "CR2")

  # Planned comparions

  CourtshipBgrd_pop_back_BR_CC <- lmer(dS ~ -1 + pop_back_BR + (1|ID), data = CourtshipBgrd_Hawaii)

     # Fit Robust model
    robust_CourtshipBgrd_pop_back_BR_CC <- clubSandwich::conf_int(CourtshipBgrd_pop_back_BR_CC, 
                                                              cluster = CourtshipBgrd_Hawaii$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_back_BR_CC <- Wald_test(CourtshipBgrd_pop_back_BR_CC, 
                                                   constraints = constrain_pairwise(c(1:8)),
                                                   cluster = CourtshipBgrd_Hawaii$ID,
                                                   vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_backCC$p_val, "bonferroni"), function(x) p_value(x))

       # Grab contrasts that we need from the robust esatimtes
      string <- c("pop_back_BRHawaii.Kenya.gular - pop_back_BRHawaii.Hawaii.gular|pop_back_BRHawaii.Kenya.midflank - pop_back_BRHawaii.Hawaii.midflank|pop_back_BRHawaii.Kenya.tailbase - pop_back_BRHawaii.Hawaii.tailbase|pop_back_BRHawaii.Kenya.topflank - pop_back_BRHawaii.Hawaii.topflank")

         result_CourtshipBgrd_pop_backCC <- result_CourtshipBgrd_pop_back_BR_CC[
                                            grep(string, result_CourtshipBgrd_pop_back_BR_CC$hypothesis),]
